    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Rushikesh Neve} % Your Name
\newcommand{\course}{Computer Science and Engineering} % Your Program
\newcommand{\phone}{7776881389} % Your Phone Number
\newcommand{\emaila}{rushikeshneve.rvn@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone}\\
 Software Engineer I & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\ {Pattern Technologies} 
 & \href{https://github.com/RushikeshNeve}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} \\  
 & \href{https://www.linkedin.com/in/rushikesh-neve-a96744212/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}

% Optimized for SDE-2 / Backend Engineer Roles
% All major content adapted for impact, clarity, and ATS compliance
% Project, AI, AWS, system design, and leadership emphasis included

% REPLACE ONLY THE EXPERIENCE SECTION BELOW WITH THIS:

\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer I}{July 2024 -- Present}
{Pattern Technologies}{Pune, India}
\resumeItemListStart
\item {Led backend architecture and feature delivery for a GenAI-powered product content optimization platform across global e-commerce marketplaces.}
\item {Engineered scalable \textbf{REST APIs} in \textbf{Node.js (Express, Restify)} and \textbf{TypeScript}, integrated with \textbf{DynamoDB}, \textbf{RethinkDB}, and \textbf{Redis} caching.}
\item {Architected and implemented a \textbf{version-controlled history system} to enable auditability and rollback of content changes.}
\item {Designed \textbf{state machines} for content lifecycle management; ensured correctness of state transitions in async flows.}
\item {Built \textbf{Excel export infrastructure} to generate brand-specific style guides and optimization reports dynamically.}
\item {Integrated \textbf{third-party task orchestration platform} to trigger async job queues based on listing triggers.}
\item {Led backend architecture for the \textbf{AI Image Generation module} with \textbf{LLM-based prompt generation} and OpenAI API integration.}
\item {Worked on observability and relevance ranking with \textbf{ElasticSearch} and OpenSearch-compatible indexing.}
\item {Co-managed a \textbf{4-member backend team}; owned design reviews, sprint planning, and mentoring.}
\item {Awarded the \textbf{Rising Star Award (2025)} for high ownership, execution speed, and cross-team impact.}
\resumeItemListEnd

\resumeSubheading
{Backend Engineering Intern}{Jan 2024 -- July 2024}
{Pattern Technologies}{Pune, India}
\resumeItemListStart
\item {Built microservice APIs for backend content optimization workflows using \textbf{Node.js} and \textbf{FastAPI}.}
\item {Integrated \textbf{OpenAI APIs} for content enrichment and keyword optimization flows; optimized token usage by caching.}
\item {Designed internal admin tools and export endpoints to support business stakeholders with brand content audits.}
\item {Worked across \textbf{AWS (Lambda, S3)}, \textbf{Redis}, \textbf{RethinkDB}, and CI/CD pipelines for microservices.}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{May 2023 -- July 2023}
{Trading Technologies}{Pune, India}
\resumeItemListStart
\item {Built a Jenkins-based release automation system for Market Data Systems (MDS), cutting manual ops by 40\%.}
\item {Extended output verification modules in \textbf{C++}, applying object-oriented design for easy test extensibility.}
\item {Reduced AWS storage usage by \textbf{25\%} through archive-level memory profiling and data TTL rules.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ----------- EDUCATION -----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Technology in Computer Engineering}{CGPA: 8.60 / 10}
{College of Engineering Pune (COEP)}{2020 -- 2024}
\resumeSubHeadingListEnd

% ----------- TECHNICAL SKILLS -----------
\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.05in, label={}]
\small{\item{
\textbf{Languages:} TypeScript, JavaScript, Python, C/C++ \\
\textbf{Frameworks / Libraries:} Node.js, Express, FastAPI, Flask, Restify \\
\textbf{Databases:} DynamoDB, RethinkDB, MongoDB, MySQL \\
% \textbf{Cloud \& DevOps:} AWS (Lambda, S3, EC2, IAM, SQS), Docker, CI/CD \\
\textbf{AI/LLM:} OpenAI API, Prompt Engineering, GenAI Workflows \\
\textbf{Tools:} Git, Postman, Jenkins, Redis, ElasticSearch, REST APIs \\
\textbf{CS Fundamentals:} Data Structures, Algorithms, OOP, OS, DBMS
}}
\end{itemize}

% ----------- PROJECTS -----------
\section{\textbf{Key Projects}}
\resumeSubHeadingListStart

\resumeProject
{AI-Based DDoS Attack Detector}{Real-time network attack classification and mitigation system}
{}{}
\begin{itemize}
  \item Developed a system to detect and prevent DDoS attacks using behavioral analysis of network traffic.
  \item Technologies: Python, Socket Programming, Scapy, Data Filtering
\end{itemize}

\resumeProject
{XV6 Kernel Threading Enhancement}{Added multithreading support to Xv6}
{}{}
\begin{itemize}
  \item Introduced kernel-level threading in the Xv6 OS using clone(), join(), and thread ID syscalls.
  \item Improved concurrency and process scheduling with thread grouping support.
  \item Technologies: C, OS Internals, Thread Management
\end{itemize}

\resumeProject
{CineManager Web App}{End-to-end Movie Ticket Booking Portal}
{}{}
\begin{itemize}
  \item Built a full-stack web app with role-based features for Admins and Customers.
  \item Enabled dynamic seat booking, user auth, and admin movie CRUD workflows.
  \item Stack: Flask, MySQL, HTML/CSS, JavaScript
\end{itemize}

\resumeSubHeadingListEnd
% %-----------EXPERIENCE-----------------
% \section{\textbf{Experience}}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Summer Internship}{Onsite}
%       {Trading Technologies}{May - July 2023}
%       \vspace{-2.0mm}
%       \resumeItemListStart
%     \item {Developed an automated release process for the Market Data System (MDS) using Jenkins, integrating new markets
%  efficiently.}
%     \item {Proficiently applied C++ object-oriented programming (OOP) to expand Jenkins’ capabilities for output compar
% ison and change detection with new markets.}
%     \item {Devised a novel memory storage optimization technique for AWS, reducing market data storage by up to 25%,
%  enhancing cost-effectiveness.}
%     % \item {Hands-on experience in cloud infrastructure provisioning, monitoring, and automation using AWS Management Console and AWS CLI.}
%     \resumeItemListEnd
    
%     \vspace{-3.0mm}
    
%     \resumeSubheading
%       {Winter Internship}{Onsite}
%       {Pattern Technologies}{Jan 2024 - Present}
%       \vspace{-2.0mm}
%       \resumeItemListStart
%     \item {Developed and implemented a comprehensive methodology for optimizing product content on e-commerce platforms, addressing key challenges such as complex algorithms, competitive landscape, and keyword research complexity.}
%     \item {Leveraged expertise in data analytics and AI technologies to design and deploy a Gen-AI model for generating optimized product content, resulting in improved visibility, customer engagement, and compliance with marketplace policies.}
%     \resumeItemListEnd
    
%     \vspace{-3.0mm}
      
%   \resumeSubHeadingListEnd
% \vspace{-5.5mm}







% %-----------Technical skills-----------------
% \section{\textbf{Technical Skills}}
% \begin{itemize}[leftmargin=0.05in, label={}]
% \small{\item{
% \textbf{Languages:} JavaScript, TypeScript, Python, C/C++ \\
% \textbf{Backend Frameworks:} Node.js, Express.js, Restify, FastAPI, Flask \\
% \textbf{Databases:} RethinkDB, DynamoDB, MongoDB, MySQL \\
% \textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda, IAM), Docker \\
% \textbf{AI / GenAI:} OpenAI API, Prompt Engineering, LLM Integrations \\
% \textbf{Caching \& Search:} Redis, ElasticSearch \\
% \textbf{Core CS:} Data Structures \& Algorithms, OOP, OS, DBMS
% }}
\end{itemize}
\vspace{-14pt}



%-----------Positions of Responsibility-----------------
\section{\textbf{Positions of Responsibility}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Web Coordinator } % Position
    {Impression- COEP, Pune} %Club,Event
    {Oct - Dec 2022} %Tenure Period \\
    \resumeItemListStart
    \item {Helped to attract close to 300 attendees to the event.}
    \item {Designed and managed the official website of COEP Impressions (Cultural-Fest).}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}




% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
